Phylodynamic inference of contact network parameters through approximate Bayesian computation

### 2016-04-20 doc/thesis/discussion.tex
Finished draft intro!
I don't know, more writing

The method behind \software{netabc} is model-agnostic, meaning that it can be
used to infer parameters of any network model, as long as it allows simulated
networks can be easily generated. We have included generators for the \gls{BA}
model discussed here, as well as the \gls{ER} and \gls{SW} network models.
Instructions for adding additional models are available in the project's online
documentation. We have made \software{netabc} publicly available at
\url{github.com/rmcclosk/netabc} under a permissive open source license, to
encourage other researchers to apply and extend our method.

>>>>

The method behind \software{netabc} is model-agnostic, meaning that it can be
used to infer parameters of any network model, as long as it allows simulated
networks can be easily generated. We have included generators for the \gls{BA}
model discussed here, as well as the \gls{ER} and \gls{WS} network models.
Instructions for adding additional models are available in the project's online
documentation. We have made \software{netabc} publicly available at
\url{github.com/rmcclosk/netabc} under a permissive open source license, to
encourage other researchers to apply and extend our method.

In retrospect, there are a few algorithmic improvements which could have been
made to \software{netabc}. Firstly, our implementation uses simple multinomial
sampling for the resampling step, as well as for generating the final sample
from the target distribution.  Several other sampling strategies have been
developed~\autocite{douc2005comparison}, and it is possible that the use of a
more sophisticated scheme might increase the algorithm's accuracy.

### 2016-04-20 doc/thesis/intro.tex
I don't know, more writing

@@

A popular method for circumventing the normalizing constant is the use of
\gls{MCMC} to obtain a sample from the posterior distribution. \Gls{MCMC} works
by defining a Markov chain whose states are indexed by possible model
parameters. The transition probability from state $\theta_1$ to state
$\theta_2$ is taken to be
\[
  \max\left(1, \frac{f(y \mid \theta_2) \pi(\theta_2) q(\theta_2, \theta_1)}
                    {f(y \mid \theta_1) \pi(\theta_2) q(\theta_1, \theta_2)} \right),
\]
where $q(\theta, \theta')$ is a symmetric \defn{proposal distribution} used in
the algorithm to generate the chain. The stationary distribution of this Markov
chain is equal to the posterior distribution on $\theta$. Therefore, if a long
enough random walk is performed on the chain, the distribution of states
visited will be a Monte Carlo approximation of $\Pr(\theta \mid y)$, from
which we can calculate statistics of interest. Actually performing this random
walk is straightforward and can be accomplished via the Metropolis-Hastings
algorithm (\cref{alg:mh}).

@@

\begin{algorithm}
  \caption{\gls{ABC}-\gls{MCMC}.}
  \begin{algorithmic}
    \State Draw $\theta$ according to $\Pr(\theta)$
    \Loop
      \State Propose $\theta'$ according to $q(\theta, \theta')$
      \State Simulate a dataset $\vec{z'}$ according to the model with
             parameters $\theta$
      \State Accept $\theta \gets \theta'$ with probability
      $\max \left( 1, 
       \dfrac{\pi(\theta') q(\theta', \theta)}
             {\pi(\theta\phantom{'}) q(\theta, \theta')} 
       \cdot \I_{A_{\varepsilon, y}}(z') \right)$
    \EndLoop
  \end{algorithmic}
  \label{alg:abcmcmc}
\end{algorithm}

@@

All the algorithms discussed in this section can be straightforwardly extended
to sample from the joint distribution
\[
  \pi_\varepsilon(\theta, z_1, \ldots, z_M \mid y),
\]
which is equivalent to associating $M$ simulated datasets to each parameter
particle instead of just one. The simulated dataset $z$ is replaced by
$z = z_1, \ldots, z_M$, and the indicator function for the
$\varepsilon$-ball around $y$ is replaced by
\[
  \sum_{k=1}^M \I_{A_{\varepsilon, y}} (z_i).
\]
For \gls{ABC}-\gls{MCMC} and \gls{ABC}-\gls{SMC}, the proposal distribution
$q(\theta, \theta') \Pr(z \mid \theta')$ is replaced by
\[
  q_i(\theta, \theta') \prod_{k=1}^M \Pr(z_i \mid \theta').
\]

>>>>

The kernel score of a pair of trees, denoted $K(T_1, T_2)$, is defined as a sum
over all pairs of nodes $(n_1, n_2)$, where $n_1$ is a node in $T_1$ and $n_2$
is a node in $T_2$. Folloting \textcite{poon2013mapping}, let $N(T)$ denote the
set of all nodes in $T$, $\nc(n)$ be the number of children of node $n$,
$c_n^{j}$ be the $j$th child of node $n$, and $l_n$ be the vector of branch
lengths connecting node $n$ to its descendants. The \defn{production rule} of
$n$ is its total number of children, and its number of leaf children. That is,
if two nodes have the same number of children and among these, the same number
of leaves, then they have the same production rule. Let $k_G(x, y)$ be a
Gaussian radial basis function of the vectors $x$ and $y$,
\[
  k_G(x, y) = \exp\left(-\frac{1}{2\sigma} \norm{x - y}_2^2\right),
\]
where $\norm{\cdot}_2$ is the Euclidian norm and $\sigma$ is a variance
parameter. The tree kernel is defined as 
\[
  K(T_1, T_2) = \sum_{n_1 \in N(T_1)} \sum{n_2 \in N(T_2)} \Delta (n_1, n_2),
\]
where
\[
  \Delta(n_1, n_2) =
  \begin{cases}
    \lambda & n_1 \text{ and } n_2 \text{ are leaves} \\
    \lambda k_G(l_{n_1}, l_{n_2}) \displaystyle\prod_{j=1}^{\nc(n_1)} \left(1 +
    \Delta(c_{n_1}^j, c_{n_2}^j) \right) & \begin{aligned} n_1 \text{ and } n_2 \text{ have the same} \\ \text{production rule} \end{aligned} \\
    0 & \text{otherwise}.

  \end{cases}
\]
Here $\lambda$ is a decay factor parameter, which penalizes large matches that
tend to dominate the kernel score. In this work, we refer to the parameters
$\lambda$ and $\sigma$ as \defn{meta-parameters}, to avoid confusing them with
model parameters we are trying to estimate.

@@

A popular method for circumventing the normalizing constant is the use of
\gls{MCMC} to obtain a sample from the posterior distribution. \Gls{MCMC} works
by defining a Markov chain whose states are indexed by possible model
parameters. The transition probability from state $\theta_1$ to state
$\theta_2$ is taken to be
\[
  \max\left(1, \frac{f(y \mid \theta_2) \pi(\theta_2) q(\theta_2, \theta_1)}
                    {f(y \mid \theta_1) \pi(\theta_2) q(\theta_1, \theta_2)} \right),
\]
where $q(\theta, \theta')$ is a symmetric \defn{proposal distribution} used in
the algorithm to generate the chain. The stationary distribution of this Markov
chain is equal to the posterior distribution on $\theta$. Therefore, if a long
enough random walk is performed on the chain, the distribution of states
visited will be a Monte Carlo approximation of $f(\theta \mid y)$, from
which we can calculate statistics of interest. Actually performing this random
walk is straightforward and can be accomplished via the Metropolis-Hastings
algorithm (\cref{alg:mh}).

@@

\begin{algorithm}
  \caption{\gls{ABC}-\gls{MCMC}.}
  \begin{algorithmic}
    \State Draw $\theta$ according to $\pi(\theta)$
    \Loop
      \State Propose $\theta'$ according to $q(\theta, \theta')$
      \State Simulate a dataset $\vec{z'}$ according to the model with
             parameters $\theta$
      \State Accept $\theta \gets \theta'$ with probability
      $\max \left( 1, 
       \dfrac{\pi(\theta') q(\theta', \theta)}
             {\pi(\theta\phantom{'}) q(\theta, \theta')} 
       \cdot \I_{A_{\varepsilon, y}}(z') \right)$
    \EndLoop
  \end{algorithmic}
  \label{alg:abcmcmc}
\end{algorithm}

@@

All the algorithms discussed in this section can be straightforwardly extended
to sample from the joint distribution
\[
  \pi_\varepsilon(\theta, z_1, \ldots, z_M \mid y),
\]
which is equivalent to associating $M$ simulated datasets to each parameter
particle instead of just one. The simulated dataset $z$ is replaced by
$z = z_1, \ldots, z_M$, and the indicator function for the
$\varepsilon$-ball around $y$ is replaced by
\[
  \sum_{k=1}^M \I_{A_{\varepsilon, y}} (z_i).
\]
For \gls{ABC}-\gls{MCMC} and \gls{ABC}-\gls{SMC}, the proposal distribution
$q(\theta, \theta') f(z \mid \theta')$ is replaced by
\[
  q_i(\theta, \theta') \prod_{k=1}^M f(z_i \mid \theta').
\]

### 2016-04-20 doc/thesis/methods.tex
I don't know, more writing

As described in \cref{sec:smc}, \software{netabc} keeps track of a population
of particles, each of which contains particular parameter values for the model
we are trying to fit. A small number of contact networks are generated for each
particle, in accordance with that particle's parameters. An epidemic is
simulated over each of these networks using Gillespie simulation, and by
keeping track of its progress, a transmission tree is obtained. Thus, each
particle becomes associated with several simulated transmission trees.  These
trees are compared to the observed tree using the phylogenetic kernel.
Particles are weighted according to the similarity of their associated
simulated trees with the true tree, with more similar trees receiving higher
weights. The particles are iteratively perturbed to explore the parameter
space, and particles with simulated trees too distant from the true tree are
periodically dropped and resampled. Once a convergence criterion is attained,
the final set of particles is used as a Monte Carlo approximation to the target
distribution of \gls{ABC}, which is assumed to resemble the posterior
distribution on model parameters (see \cref{sec:abc}). A graphical schematic of
this algorithm is given in \cref{fig:abcsmc}.

@@

The tree kernel developed by \textcite{poon2013mapping} provides a
comprehensive similarity score between two phylogenetic trees, via the
dot-product of the two trees' feature vectors in the infinite-dimensional space
of all possible subset trees with branch lengths (see \cref{subsec:treeshape}).
The kernel was implemented using the fast algorithm developed by
\textcite{moschitti2006making}. First, the number of leaf children of each
node, also known as its \defn{production rule}, is recorded. The nodes of both
trees are ordered by production rule, and a list of pairs of nodes sharing the
same production rule is created. These are the nodes for which the value of the
tree kernel must be computed - all other pairs have a value of zero. The pairs
to be compared are then re-ordered so that the child nodes are always evaluated
before their parents. Due to its recursive definition, ordering the pairs in
this way allows the tree kernel to be computed by dynamic programming. The
complexity of this implementation is $O(|T_1||T_2|)$, where $|T|$ counts the
number of nodes in the tree $T$.

@@

I implemented the adaptive \gls{SMC} algorithm for \gls{ABC} developed by
\textcite{del2012adaptive}. This algorithm is similar to the reference
\gls{ABC}-\gls{SMC} algorithm described in \cref{subsec:abcalg}, except that
the sequence of tolerances $\varepsilon_i$ is automatically determined rather
than specified in advance. The tolerances are chosen such that the \gls{ESS} of
the particle population, which indicates the quality of the Monte Carlo
approximation (see \cref{subsec:sis}), decays at a controlled rate. This
prevents the Monte Carlo approxmiation from collapsing by the variance in
weights growing too large. A single parameter $\alpha$ (not to be confused with
the \gls{BA} model parameter) controls the decay rate, with $\varepsilon_i$
being chosen to satisfy
\[
  \ESS(w_i) = \alpha \ESS(w_{i-1}).
\]
Here, $w_i$ is the vector of weights at the $i$th step. Note that, since $w_i$
depends on $\varepsilon_i$, this equation solves for the updated weights and
the updated tolerance simultaneously. As pointed out by
\textcite{del2012adaptive}, the equation has no analytic solution, but can be
solved numerically by bisection. The forward kernels $K_i$ are taken to be
\gls{MCMC} kernels with stationary distributions $\pi_{\varepsilon_i}$ and
proposal distributions
\[
  q_i(\theta, \theta') \prod_{k=1}^M \Pr(X_i^{(k)'} \mid \theta'),
\]
where $\theta$ is the vector of model parameters and $X_k$ are $M$ datasets
simulated according to $\theta$. In our implementation, $q$ is a Gaussian
proposal with variance equal to twice the empirical variance of the particles,
following~\autocite{beaumont2009adaptive, del2012adaptive}. The backwards
kernels are
\[
  L_{i-1}(z', z) = \frac{\pi_n(z)K(z, z')}{\pi_n(z')}.
\]
When substituted into \cref{eq:smcwt}, the forward kernels $K(z, z')$ and
densities $\pi_n(z')$ cancel out, and we are left with the weight update
\begin{align*}
  w(z') 
    &\propto w(z) \frac{\pi_n(z \mid y)}{\pi_{n-1}(z \mid y)} \\
    &= w(z) \frac{\pi(z) \pi_n(y \mid z)}{\pi(z) \pi_{n-1}(y \mid z)} \\
    &= w(z) \frac{\sum_{k=i}^M \I_{A_{\varepsilon_n, y}}(x_k)}
            {\sum_{k=i}^M \I_{A_{\varepsilon_{n-1}, y}}(x_k)}.
\end{align*}
The algorithm may be stopped when one of two termination conditions is reached.
The user may specify a final tolerance $\varepsilon$, or a final acceptance
rate of the \gls{MCMC} kernel. The latter stops the algorithm when the
particles are not moving around very much, implying little change in the
estimated target.

@@

\subsubsection*{Characterization of power-law exponent in Barab\'asi-Albert networks}

Most studies of social network or transmission network
parameters~\autocite[e.g.][]{liljeros2001web, jones2003assessment,
schneeberger2004scale, brown2011transmission} report the coefficient
\gls{gamma} of the power law degree distribution. To make our results
comparable to previous work, we used simulated networks to investigate the
relationship between the \gls{BA} model parameters and \gls{gamma}. A network
was simulated for each combination of parameters listed in
\cref{tab:gammaexpt}. A power law distribution was fitted to the degree
distribution of each simulated network using the \software{fit\_power\_law}
function in \software{igraph} with the `R.mle' implementation. We fitted a
\gls{GLM} with Gamma-distributed errors and a log link function to the observed
distribution of \gls{gamma} values, with \gls{alpha}, \gls{m}, \gls{N}, and all
possible interaction terms as predictors.

@@

We downloaded all sequences associated with each published study from GenBank.
For the \textcite{novitsky2014impact} data, each \textit{env} sequence was
aligned pairwise to the HXB2 reference sequence (GenBank accession number
HIVHXB2CG) and the hypervariable regions were clipped out with
\software{BioPython} version 1.66+~\autocite{cock2009biopython}. Sequences were
multiply aligned using \software{MUSCLE} version 3.8.31
\autocite{edgar2004muscle}, and alignments were manually inspected with
\software{Seaview} version 4.4.2 \autocite{gouy2010seaview}. Phylogenies were
constructed from the nucleotide alignments by approximate maximum likelihood
using \software{FastTree2} version 2.1.7 with the \gls{GTR} model. Transmission
trees were estimated by rooting and time-scaling the phylogenies by root-to-tip
regression, using a modified version of Path-O-Gen (distributed as part of
BEAST~\autocite{drummond2007beast}) as described
previously~\autocite{poon2015phylodynamic}.

>>>>

As described in \cref{sec:smc}, \software{netabc} keeps track of a population
of particles $x^{(k)}$, each of which contains particular parameter values
$\theta^{(k)}$ for the model we are trying to fit. A small number of contact
networks $z^{(k)}$ are generated for each particle, in accordance with that
particle's parameters. An epidemic is simulated over each of these networks
using Gillespie simulation, and by keeping track of its progress, a
transmission tree is obtained. Thus, each particle becomes associated with
several simulated transmission trees. These trees are compared to the observed
tree using the phylogenetic kernel. Particles are weighted according to the
similarity of their associated simulated trees with the true tree, with more
similar trees receiving higher weights. The particles are iteratively perturbed
to explore the parameter space, and particles with simulated trees too distant
from the true tree are periodically dropped and resampled. Once a convergence
criterion is attained, the final set of particles is used as a Monte Carlo
approximation to the target distribution of \gls{ABC}, which is assumed to
resemble the posterior distribution on model parameters (see \cref{sec:abc}). A
graphical schematic of this algorithm is given in \cref{fig:abcsmc}.

@@

The tree kernel developed by \textcite{poon2013mapping} provides a
comprehensive similarity score between two phylogenetic trees, via the
dot-product of the two trees' feature vectors in the infinite-dimensional space
of all possible subset trees with branch lengths (see \cref{subsec:treeshape}).
The kernel was implemented using the fast algorithm developed by
\textcite{moschitti2006making}. First, the production rule of each node, which
is the total number of children and the number of leaf children, is recorded.
The nodes of both trees are ordered by production rule, and a list of pairs of
nodes sharing the same production rule is created. These are the nodes for
which the value of the tree kernel must be computed - all other pairs have a
value of zero. The pairs to be compared are then re-ordered so that the child
nodes are always evaluated before their parents. Due to its recursive
definition, ordering the pairs in this way allows the tree kernel to be
computed by dynamic programming. The complexity of this implementation is
$O(|T_1||T_2|)$, where $|T|$ counts the number of nodes in the tree $T$.

The tree kernel cannot be used directly as a distance measure for \gls{ABC},
since it is maximized, not minimized, when the two trees being compared are the
same. Therefore, we defined the distance between two trees as
\[
  \rho(T_1, T_2) = 1 - \frac{K(T_1, T_2)}{\sqrt{K(T_1, T_1) K(T_2, T_2)}},
\]
which is a number between 0 and 1 minimized when $T_1 = T_2$. This is similar
to the normalization used by \textcite{collins2002new, poon2013mapping}.

@@

We implemented the adaptive \gls{SMC} algorithm for \gls{ABC} developed by
\textcite{del2012adaptive}. This algorithm is similar to the reference
\gls{ABC}-\gls{SMC} algorithm described in \cref{subsec:abcalg}, except that
the sequence of tolerances $\varepsilon_i$ is automatically determined rather
than specified in advance. The tolerances are chosen such that the \gls{ESS} of
the particle population, which indicates the quality of the Monte Carlo
approximation (see \cref{subsec:sis}), decays at a controlled rate. This
prevents the Monte Carlo approxmiation from collapsing by the variance in
weights growing too large. A single parameter $\alpha$ (not to be confused with
the \gls{BA} model parameter) controls the decay rate, with $\varepsilon_i$
being chosen to satisfy
\[
  \ESS(w_i) = \alpha \ESS(w_{i-1}).
\]
Here, $w_i$ is the vector of weights at the $i$th step. Note that, since $w_i$
depends on $\varepsilon_i$, this equation solves for the updated weights and
the updated tolerance simultaneously. As pointed out by
\textcite{del2012adaptive}, the equation has no analytic solution, but can be
solved numerically by bisection. The forward kernels $K_i$ are taken to be
\gls{MCMC} kernels with stationary distributions $\pi_{\varepsilon_i}$ and
proposal distributions
\[
  q_i(\theta, \theta') \prod_{k=1}^M \Pr(z_i^{(k)'} \mid \theta'),
\]
where $\theta$ is the vector of model parameters and $z_k$ are $M$ datasets
simulated according to $\theta'$. In our implementation, $q$ is either a
Gaussian proposal for continuous parameters, or a Poisson proposal for discrete
parameters. For the Poisson proposals, the number of steps to move the particle
is drawn from a Poisson distribution, and the direction in which to move the
particle is chosen uniformly at random. For both proposals, the variance was
set equal to twice the empirical variance of the particles,
following~\autocite{beaumont2009adaptive, del2012adaptive}. The backwards
kernels are
\[
  L_{i-1}(x', x) = \frac{\pi_n(x)K(x, x')}{\pi_n(x')}.
\]
When substituted into \cref{eq:smcwt}, the forward kernels $K(x, x')$ and
densities $\pi_n(x') = \pi_{\varepsilon_n}(x')$ cancel out, and we are left
with the weight update 
\begin{align*}
  w_i(x) 
    &\propto w_{i-1}(x) \frac{\pi_n(x \mid y)}{\pi_{i-1}(x \mid y)} \\
    &= w_{i-1}(x) \frac{\pi(x) \pi_i(y \mid x)}{\pi(x) \pi_{i-1}(y \mid x)} \\
    &= w_{i-1}(x) \frac{\sum_{k=i}^M \I_{A_{\varepsilon_i, y}}(z_k)}
            {\sum_{k=i}^M \I_{A_{\varepsilon_{i-1}, y}}(z_k)}.
\end{align*}
In other words, when the distance threshold $\varepsilon_{i-1}$ is contracted
to $\varepsilon_i$, the particles' weights are multiplied by the proportion of
simulated datasets which are still inside the new threshold. The algorithm may
be stopped when one of two termination conditions is reached. The user may
specify a final tolerance $\varepsilon$, or a final acceptance rate of the
\gls{MCMC} kernel. The latter condition stops the algorithm when the particles
are not moving around very much, implying little change in the estimated
target.

@@

%\subsubsection*{Characterization of power-law exponent in Barab\'asi-Albert networks}
%
%Most studies of social network or transmission network
%parameters~\autocite[e.g.][]{liljeros2001web, jones2003assessment,
%schneeberger2004scale, brown2011transmission} report the coefficient
%\gls{gamma} of the power law degree distribution. To make our results
%comparable to previous work, we used simulated networks to investigate the
%relationship between the \gls{BA} model parameters and \gls{gamma}. A network
%was simulated for each combination of parameters listed in
%\cref{tab:gammaexpt}. A power law distribution was fitted to the degree
%distribution of each simulated network using the \software{fit\_power\_law}
%function in \software{igraph} with the `R.mle' implementation. We fitted a
%\gls{GLM} with Gamma-distributed errors and a log link function to the observed
%distribution of \gls{gamma} values, with \gls{alpha}, \gls{m}, \gls{N}, and all
%possible interaction terms as predictors.

@@

We downloaded all sequences associated with each published study from GenBank.
For the \textcite{novitsky2014impact} data, each \textit{env} sequence was
aligned pairwise to the HXB2 reference sequence (GenBank accession number
K03455) and the hypervariable regions were clipped out with
\software{BioPython} version 1.66+~\autocite{cock2009biopython}. Sequences were
multiply aligned using \software{MUSCLE} version 3.8.31
\autocite{edgar2004muscle}, and alignments were manually inspected with
\software{Seaview} version 4.4.2 \autocite{gouy2010seaview}. Phylogenies were
constructed from the nucleotide alignments by approximate maximum likelihood
using \software{FastTree2} version 2.1.7 with the \gls{GTR} model. Transmission
trees were estimated by rooting and time-scaling the phylogenies by root-to-tip
regression, using a modified version of Path-O-Gen (distributed as part of
BEAST~\autocite{drummond2007beast}) as described
previously~\autocite{poon2015phylodynamic}.

### 2016-04-20 doc/thesis/preface.tex
Wrote discussion mostly
I don't know, more writing

This work was conducted at the BC Centre for Excellence in HIV/AIDS under the
supervision of Dr. Art Poon. I wrote the code, performed the experiments, and
wrote the thesis. Dr. Richard Liang assisted with the development of the
Gillespie simulation algorithm.

A version of chapters 2 and 3 has been submitted for publication in Molecular
Biology and Evolution, with the title ``Phylogenetic estimation of contact
network parameters with kernel-ABC''. A presentation with the same title was
given at the 23rd HIV Dynamics and Evolution meeting on April 25, in Woods
Hole, Massachussets, USA.

>>>>

The initial idea to use kernel approximate Bayesian computation to infer
contact network model parameters was Dr. Poon's. The tree kernel was originally
developed by Dr. Poon, but the version used here was implemented by me to
improve computational efficiency. The idea to apply sequential Monte Carlo is
credited to Dr. Alexandre Bouchard-C\^ot\'e. Dr. Sarah Otto suggested the
experiments involving a network with a heterogeneous $\alpha$ parameter and
peer-driven sampling. Dr. Richard H. Liang provided guidance in the development
of the Gillespie simulation algorithm. The \software{netabc} program, and all
supplementary analysis programs, were written by me.

A version of chapter 2 has been submitted for publication in Virus Evolution
with the title ``Reconstructing network parameters from viral phylogenies.'' A
presentation entitled ``Phylodynamic inference of contact network parameters
with kernel-ABC'' was given based on chapter 2 at the 23rd HIV Dynamics and
Evolution meeting on April 25, in Woods Hole, Massachussets, USA.

Throughout this work, the pronouns \textit{we} and \textit{our} refer to
Rosemary M. McCloskey unless otherwise stated.

### 2016-04-20 doc/thesis/results.Rnw
I don't know, more writing

The average error for \gls{m} was
    \Sexpr{d[parameter == "m", round(mean(error), 2)]},
on a grid from 1 to 6; this error was positively correlated with increasing
\gls{m}
    (Spearman's $\rho$ = \Sexpr{value.cor["m", round(estimate, 2)]},
     $p = \Sexpr{value.cor["m", pp(p.value)]}$).
This positive correlation was apparently due to the much lower error for
\gls{m} = 1 and 2 than for the other $m$ values 
    (mean errors 
    \Sexpr{d[parameter == "m" & true_value <= 2, round(mean(error), 2)]} 
    for $m \leq 2$ vs. 
    \Sexpr{d[parameter == "m" & true_value > 2, round(mean(error), 2)]} 
    for $m > 2$, \cref{fig:gridm}).
The value $m = 1$ causes the network to take on a distinct shape relative to
higher \gls{m} values, namely a tree (\textit{i.e.} there are no cycles,
see \cref{subsec:treeshape}). The average error for \gls{N} was 
    \Sexpr{d[parameter == "N", round(mean(error))]},
on a grid from 1000 to 15000, and was positively correlated with the true value
of \gls{N}
    (Spearman's $\rho$ = \Sexpr{value.cor["N", round(estimate, 2)]},
    $p \Sexpr{value.cor["N", pp(p.value)]}$).

>>>>

The average error for \gls{m} was
    \Sexpr{d[parameter == "m", round(mean(error), 2)]},
on a grid from 1 to 6; this error was positively correlated with increasing
\gls{m}
    (Spearman's $\rho$ = \Sexpr{value.cor["m", round(estimate, 2)]},
     $p = \Sexpr{value.cor["m", pp(p.value)]}$).
This positive correlation was apparently due to the much lower error for
\gls{m} = 1 and 2 than for the other $m$ values 
    (mean errors 
    \Sexpr{d[parameter == "m" & true_value <= 2, round(mean(error), 2)]} 
    for $m \leq 2$ vs. 
    \Sexpr{d[parameter == "m" & true_value > 2, round(mean(error), 2)]} 
    for $m > 2$, \cref{fig:gridm}).
The value $m = 1$ causes the network to take on a distinct shape relative to
higher \gls{m} values, namely a tree (\textit{i.e.} there are no cycles,
see \cref{subsec:treeshape}). The average error for \gls{N} was 
    \Sexpr{d[parameter == "N", round(mean(error))]},
on a grid from 1000 to 15000, and was positively correlated with the true value
of \gls{N}
    (Spearman's $\rho$ = \Sexpr{value.cor["N", round(estimate, 2)]},
    $p\ \Sexpr{value.cor["N", pp(p.value)]}$).
